---
title: "DDSWK10HW"
author: "Chiranjeevi Mallavarapu"
date: "7/20/2017"
output: 
  html_document: 
    keep_md: true
---

# This is HW10 for Week 10

---

# Load the required library

```{r }
library(ggplot2)
```
# 1) Load data from	http://stat.columbia.edu/~rachel/datasets/nyt1.csv


```{r }
knitr::opts_chunk$set(echo = TRUE, include = TRUE)
fileLocation <- "http://stat.columbia.edu/~rachel/datasets/nyt1.csv"
data1 <- read.csv(url(fileLocation))
```

# 2) Create a new variable ageGroup that categorizes age into following groups: < 18, 18–24, 25–34, 35–44, 45–54, 55–64 and 65+.

```{r }
knitr::opts_chunk$set(echo = TRUE, include = TRUE)
data1$ageGroup  <- cut(data1$Age, c(-Inf, 18, 24, 34, 44, 54, 64, Inf))
levels(data1$ageGroup) <- c("<18", "18-24", "25-34", "35-44", "45-54", "55-64", "65+")
head(data1)
```

# 3) Use sub set of data called “ImpSub” where Impressions > 0 ) in your data set.


```{r }
knitr::opts_chunk$set(echo = TRUE, include = TRUE)
ImpSub <- subset(data1, Impressions>0)
summary(ImpSub)

```

# 4) Create a new variable called click-through-rate (CTR = click/impression).


```{r }
knitr::opts_chunk$set(echo = TRUE, include = TRUE)
ImpSub$CTR <- ImpSub$Clicks/ImpSub$Impressions
head(ImpSub)
```

# 5) Plot distributions of number impressions and click-through-rate (CTR = click/impression) for the age groups.


```{r }
knitr::opts_chunk$set(echo = TRUE, include = TRUE)
ggplot(ImpSub, aes(x=Impressions, fill=ageGroup))+   labs(title="Impressions by age group")+geom_histogram(binwidth=1)
ggplot(ImpSub, aes(x=CTR, fill=ageGroup))+   labs(title="CTR by age group")+geom_histogram(binwidth=0.1)

```

# 6) Define a new variable to segment users based on click -through-rate (CTR) behavior CTR< 0.2, 0.2<=CTR <0.4, 0.4<= CTR<0.6, 0.6<=CTR<0.8, CTR>0.8	

```{r }
knitr::opts_chunk$set(echo = TRUE, include = TRUE)
ImpSub$CTR_Group <- cut(ImpSub$CTR, c(-Inf,0.2, 0.4,0.6, 0.8, Inf),right = FALSE)
levels(ImpSub$CTR_Group) <- c("<0.2", "0.2-0.4", "0.4-0.6", "0.6-0.8", "0.8+")
head(ImpSub)
```

# 7) Get the total number of Male, Impressions, Clicks and Signed_In (0=Female, 1=Male)

```{r }
knitr::opts_chunk$set(echo = TRUE, include = TRUE)
sapply(ImpSub[,c(2,3,4,5)],sum)
```

# 8) Get the mean of Age, Impressions, Clicks, CTR and percentage of males and signed_In 

```{r }
knitr::opts_chunk$set(echo = TRUE, include = TRUE)
sapply(ImpSub[,c(1,2,3,4,5,7)],mean)
```

# 9) Get the means of Impressions, Clicks, CTR and percentage of males and signed_In  by AgeGroup.


```{r }
knitr::opts_chunk$set(echo = TRUE, include = TRUE)
aggregate(ImpSub[,c(2,3,4,5,7)], by=list(Category=ImpSub$ageGroup), FUN=mean)

```

# 10) Create a table of CTRGroup vs AgeGroup counts.


```{r }
knitr::opts_chunk$set(echo = TRUE, include = TRUE)
CountAgeGrp.tab <- table(ImpSub$ageGroup,ImpSub$CTR_Group)
CountAgeGrp.tab
```

# 11) Plot distributions of number impressions and click-through-rate (CTR = click/impression) for the age groups


```{r }
knitr::opts_chunk$set(echo = TRUE, include = TRUE)
# Pls. refer to question 5)
```

# 12) One more plot you think which is important to look at.I am choosing to plot count of count by Age filled by CTR to is which age is most active 

```{r }
knitr::opts_chunk$set(echo = TRUE, include = TRUE)
AgeClickNZ <- ImpSub[ImpSub$Age >0 & ImpSub$CTR >0,]
ggplot(AgeClickNZ, aes(x=Age, fill=CTR_Group))+   labs(title="Counts by age filled in with CTR")+geom_histogram(binwidth=5)

```

## Seems like mostly people aged 60 years are highly active 